Enrich the datasets with new columns.

### 2020-08-27 inst/analysis/enrich_dataset.Rmd
Getting rid of the -finals.fst

The analysis is being performed on a dataset read from file `r CALLS_FINAL_FILE`.

```{r file-info, echo=FALSE}
file_info(CALLS_FINAL_FILE)
```

```{r load-data, echo=FALSE}
eval_calls_raw <-
    read_fst(CALLS_FINAL_FILE) %>%
    as_tibble() %>%
    mutate(corpus = "cran")

eval_calls_kaggle_raw <- 
  read_fst(KAGGLE_CALLS_FINAL_FILE) %>%
  as_tibble() %>% 
  mutate(corpus = "kaggle")

@@

```{r add_package}
eval_calls <- eval_calls %>% add_package()
```

>>>>

The analysis is being performed on a dataset read from file `r CALLS_FILE`.

```{r file-info, echo=FALSE}
file_info(CALLS_FILE)
```

```{r load-data, echo=FALSE}
corpus <- read_fst(CORPUS_DETAILS_FILE)

eval_calls_raw <-
    read_fst(CALLS_FILE) %>%
    as_tibble() %>%
    mutate(
      package=basename(dirname(dirname(file))),
      corpus="cran"
    ) %>%
    semi_join(corpus, by="package") # There might be more packages traced than what is in the corpus

eval_calls_kaggle_raw <- 
  read_fst(KAGGLE_CALLS_FILE) %>%
  as_tibble() %>% 
  mutate(
    package=basename(dirname(file)),
    corpus="kaggle"
  )

@@

```{r add_package}
# The package is already added when the files are loaded
#eval_calls <- eval_calls %>% add_package()
```
